\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    {#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\Projects}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------------------------------------------------------------------------------------------------------------------%
%------------------------------------------------------------------RESUME---------------------------------------------------------------------------%
%-------------------------------------------------------------------------------------------------------------------------------------------------------%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://ty-irving.com/}{\Large Ty Irving}} & \href{mailto:tyirving1@gmail.com}{tyirving1@gmail.com}\\
  \href{https://ty-irving.com/}{ty-irving.com} & +1-403-992-7815 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Calgary}{Calgary, AB}
      {Bachelor of Computer Science}{Sep. 2020 -- Apr. 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Calgary Public Library}{Calgary, AB}
      {Student Intern}{Jun 2022 - Aug 2022}
      \resumeItemListStart
        \resumeItem{}
          { Developed forms with React that are in production for both staff and members of the website reducing time of tasks by 50\% while working with Azure apps.}
        \resumeItem{}
	          { Converted form template from the original JavaScript template to the new template for use in future forms, template was converted
	          to TypeScript. }
        \resumeItem{}
          { Collaborated and worked with team members and participated in 100\% of the daily meetings for current projects. }
      \resumeItemListEnd


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

         
          \resumeSubheading
      {Ticket System (Ongoing)}{}
      {React.JS, TypeScript, SASS, Auth0, Go }{}
      \resumeItemListStart
        \resumeItem{}
          { Planned and developed a Ticket System using a REST API that allows for the creation of tickets and handling of tickets by both customers and support that is made with React, TypeScript.}
        \resumeItem{}
          {Innovated and created a useful user interface design that allows users to engage and properly understand how the system works through the graphical interface.}
        \resumeItem{}
          {Implemented Auth0 to streamline account creation and manage user authentication.}
      \resumeItemListEnd
      
    \resumeSubheading
      {\href{https://github.com/Ty-Irving/pathfinder}{Pathfinding Visualization}}{}
      {React.JS, SASS}{}
      \resumeItemListStart
        \resumeItem{}
          { Designed a pathfinding visualization webpage that allows for visualization of multiple different types of pathfinding algorithms built with React.}
      \resumeItemListEnd
      
          \resumeSubheading
       {\href{https://github.com/Ty-Irving/Schedule_Viewer}{Schedule Viewer }}{}
      {JS, CSS3, HTML5, JQuery, Django}{}
      \resumeItemListStart
        \resumeItem{}
          { Led a team to create a schedule viewer for managers and employees to create and view schedules along with clocking into work and numerous other features while using Postman to document requests made to the database using the REST API.}
        \resumeItem{}
          {Participated and led multiple meetings to assign and help teamates with sections of the project.}
      \resumeItemListEnd
      
           \resumeSubheading
      { \href{https://ty-irving.com}{Personal Website Portfolio } }{}
      { React.JS, SASS }{}
      \resumeItemListStart
        \resumeItem{}
          { Built and hosted personal website portfolio that includes information about me and numerous projects.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Web Proxy }{}
      { C }{}
      \resumeItemListStart
        \resumeItem{}
          { Created a web proxy that acts as an intermediary between users and webpages changing images and text on specific webpages by parsing, altering, and returning http requests using socket programming.}
      \resumeItemListEnd
            
      
  \resumeSubHeadingListEnd


%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: JavaScript, Java, TypeScript, C, SQL, Go, Python, LaTeX}
   }
   \item{
   \textbf{Technologies}{: React, AWS, Azure, Django, JQuery, Git}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}